What do incoming university students believe about open science practices in

### 2021-02-10 analysis/Manuscript.Rmd
add notes about qual demographic variables

# once qual responses are coded, I will need to return here to 
 # include details about which univrsity the participant is enrolled in
 # name of qualification
 # major

>>>>

# once qual responses are coded, I will need to return here to 
 # include details about which univrsity the participant is enrolled in
 # name of qualification
 # major [how many are majoring in psyc; NAs; will decide later?]
